---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# powder

**Author:** [Andree Valle Campos](https://twitter.com/avallecam) <a href="https://orcid.org/0000-0002-7779-481X" target="orcid.widget">
<image class="orcid" src="https://members.orcid.org/sites/default/files/vector_iD_icon.svg" height="16"></a>
<br/>
**License:** [MIT](https://opensource.org/licenses/MIT)<br/>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/powder)](https://cran.r-project.org/package=powder)
<!-- badges: end -->

## Overview

The goal of `powder` is to complement __power__ and __sample size__ calculations:

- for more than one set of parameters, and

- create tidy output tables and plots from them.  

## Installation

You can install the developing version of `powder` using:

```r
if(!require("devtools")) install.packages("devtools")
devtools::install_github("avallecam/powder")
```

<!--

You can install the released version of powder from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("powder")
```

-->

## Structure

`powder` consist of three main functions:

- `pwr_grid`: creates a tibble from all combination of input parameters using `tidyr::expand_grid`.

- `pwr_tidy`: creates a `broom::tidy()` output from the calculations of all input parameters using `purrr::pmap`.

- `pwr_plot`: create a `ggplot` with input parameters and calculated value (sample size, power or effect size)

## Example

This is a basic example which shows you how to solve a common problem:

```{r example,eval=TRUE,message=FALSE}
library(tidyverse)
library(magrittr)
library(broom)
library(pwr)
library(powder)
```

### with one set of parameters

```{r}
diff <- 10
sigma <- 10
delta <- diff/sigma

pwr.t.test(d = delta, power = 0.8, type = "one.sample") %>% tidy()
# power.t.test(d = delta, power = 0.8, type = "one.sample") %>% tidy()
# pwr.t.test(d = delta, power = 0.8, type = "one.sample") %>% plot()
```

### with more than one set of parameters

#### sample size

```{r}
# stata
# power onemean 20, diff(10 20 30) sd(10 12.5 15)
eg1 <- pwr_grid(n = NULL,
                diff = c(10,20,30),
                sigma = c(10,12.5,15),
                d = NULL,
                sig.level = 0.05,
                power = 0.8,
                type = "one.sample",
                alternative = "two.sided")

#create tidytable
eg1 %>% pwr_tidy(test_function = pwr.t.test)

#create ggplot
eg1 %>%
  pwr_tidy(test_function = pwr.t.test) %>%
  pwr_plot(x = diff,y = n,group = sigma)
```

#### power

```{r}
# stata
# power onemean 20, diff(5 (5) 15) sd(10) n(10 (2) 20)
eg2 <- pwr_grid(n = seq(from = 10,to = 20,by = 2),
                diff = seq(from = 5,to = 15,by = 5),
                sigma = 10,
                d = NULL,
                sig.level = 0.05,
                #power = 0.8,
                type = "one.sample",
                alternative = "two.sided")

#create tidytable
eg2 %>% pwr_tidy(test_function = pwr.t.test)

#create ggplot
eg2 %>%
  pwr_tidy(test_function = pwr.t.test) %>%
  pwr_plot(x = n,y = power,group=diff)
```

## References

Stephane Champely (2018). pwr: Basic Functions for Power
  Analysis. R package version 1.2-2.
  https://CRAN.R-project.org/package=pwr

## Citation

```{r}
citation("powder")
```
